Visual Analysis of Ligand Trajectories in Molecular Dynamics

### 2018-09-27 paper.tex
intro finished and abstract

%% Abstract section.
\abstract{TODO} % end of abstract

@@

\textcolor{red}{TODO finish that}

>>>>

%% Abstract section.
\abstract{
Exploration of protein reactivity with other molecules plays a crucial role in many biochemical research disciplines, including protein engineering and drug design.
In many cases, a small molecule (ligand) reacts with the protein in its deeply buried active site. 
As the ligand has to be transported to this site from the protein outer environment, it is crucial to find a feasible trajectory, which the ligand can follow.
There are several in-silico methods, enabling to calculate potential trajectories. 
They usually produce large ensembles of trajectories which have to be further explored by the biochemists who are trying to assess their relevance. 
This decision is based on many parameters of the trajectories which have to be taken into account.
This makes the exploration very demanding as the biochemists have to analyze the multidimensional data about trajectories.
Without proper visual support, this process is very complicated and time demanding.
In this paper, we introduce our tool for visual analysis of ligand trajectories and their various properties.
The tool has been designed in tight collaboration with the domain experts in order to address their needs as much as possible.
It is composed of several linked views, enabling interactive exploration and filtering of trajectories.
The tool consists of a set of 2D views and the 3D view.
It utilizes the concept of a scatterplot matrix for communicating different properties of the trajectories.
\textcolor{red}{TODO describe in one sentence the other views as well}
The usefulness of the tool is demonstrated on two case studies, conducted by the collaborating protein engineers.
} % end of abstract

@@

In the following, we are first discussing techniques and methods related to our approach and then we describe our tool in detail. 
This is followed by the demonstration of the usefulness of our tool on two case studies, performed on real scenarios and data from the latest research of our collaborating protein engineers.
